---
title: "Investigation of food-borne disease outbreaks"
author: "Thibaut Jombart"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteEngine{rmarkdown::render}
  %\VignetteIndexEntry{Investigation of food-borne disease outbreaks.}
  \usepackage[utf8]{inputenc}
---


```{r setup, echo=FALSE}
# set global chunk options: images will be 7x7 inches
knitr::opts_chunk$set(fig.width=7, fig.height=7, fig.path="figs/")
options(digits = 4)
```
*dibbler*: Investigation of food-borne disease outbreaks.

=================================================
*dibbler* provides tools for investigating food-borne outbreaks with (at least partly) known food distribution networks, and genetic information on the cases.
This document provides an overview of the package's content.


Installing *dibbler*
-------------
To install the development version from github:
```{r install, eval=FALSE}
library(devtools)
install_github("thibautjombart/dibbler")
```

The stable version can be installed from CRAN using:
```{r install2, eval=FALSE}
install.packages("dibbler")
```

Then, to load the package, use:
```{r load}
library("dibbler")
```


A short demo
------------------
Here is a short demonstration of the package using a dummy dataset.
